Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide

### 2018-05-09 draft/accordionComplexSurfaces.tex
essai
adresse Sibylle
sketch of the content

% accordion and zigzag complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\faces}{\mathcal{F}} % faces of a dissection

@@

\title{Accordion complexes versus non-kissing complexes}

@@

\author{Sibylle Schroll}
\address[Sibylle Schroll]{}
\email{}
\urladdr{\url{}}

@@

\subsection{Accordions and zigzags}

Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is ...
\end{definition}

\begin{definition}
\label{def:zigzag}
A \defn{$\dissection\dual$-zigzag} is ...
\end{definition}

@@

\begin{remark}
The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually.
\end{remark}

\newpage

>>>>

% accordion and zigzag complexes
\newcommand{\surface}{\mathcal{S}} % an orientable surface
\newcommand{\dual}{^*} % duality
\newcommand{\dissection}{\mathrm{D}} % dissection of a marked surface
\newcommand{\faces}{\mathcal{F}} % faces of a dissection
\renewcommandx{\AC}[1][1=\dissection]{\mathcal{K}_{\mathrm{acc}}(#1)} % accordion complex
\newcommandx{\ZC}[1][1=\dissection\dual]{\mathcal{K}_{\mathrm{zz}}(#1)} % zigzag complex

@@

\title{Accordion / zigzag / non-kissing / support $\tau$-tilting complexes all coincide}

@@

\author{Sibylle Schroll}
\address[Sibylle Schroll]{}
\email{schroll@leicester.ac.uk}
\urladdr{\url{}}

@@

\begin{definition}
Interior points, blossom points.
Half-edges.

We consider a set~$B$ of points on the boundary of the surface~$\surface$ such that~$B$ and~$M \cup M\dual$ alternate along the boundary of~$\surface$.
The points of~$B$ are called the \defn{blossom points}.
\vincent{I am tempted to define here the interior points and blossom points and to only consider arcs passing though these points. Still need to think about it.}
\end{definition}

Let~$\surface$ be a surface with two sets~$M$ and~$M\dual$ of marked points and two dual dissections~$\dissection$ and~$\dissection\dual$.
Let~$I$ denote the interior points and $B$ the blossom points.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
\end{definition}

\begin{definition}
\label{def:accordionComplex}
The \defn{$\dissection$-accordion complex}~$\AC$ is the simplicial complex of pairwise non-crossing $\dissection$-accordions.
\vincent{Reduced accordion complex.}
\end{definition}

\begin{definition}
\label{def:zigzag}
A \defn{$\dissection\dual$-zigzag} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
\end{definition}

\begin{definition}
\label{def:zigzagComplex}
The \defn{$\dissection\dual$-zigzag complex}~$\ZC$ is the simplicial complex of pairwise non-crossing $\dissection$-zigzags.
\vincent{Reduced zigzag complex.}
\end{definition}

@@

\begin{proposition}
\label{prop:accordionsZigzags}
For two dual dissections~$\dissection$ and~$\dissection\dual$, the $\dissection$-accordions are precisely the $\dissection\dual$-zigzags and the $\dissection$-accordion complex coincides with the $\dissection\dual$-zigzag complex.
\end{proposition}

\begin{remark}
To clearly visualize Proposition~\ref{prop:accordionsZigzags}, we follow the convention to draw the $\dissection$-accordions (resp.~$\dissection\dual$-zigzags) so that they intersect the arcs of~$\dissection$ (resp.~of~$\dissection\dual$) only at the intersection points of the arcs of~$\dissection$ with the arcs of~$\dissection\dual$.
\vincent{That is interior points}
\end{remark}

\begin{remark}
The $\dissection$-zigzags and the $\dissection\dual$-accordions are defined dually and also coincide.
\end{remark}

\begin{remark}
A quick disclaimer about accordion complexes and zigzag complexes of arbitrary dissections.
As stated in Proposition~\ref{prop:conditionsDualDissections}, a dissection~$\dissection$ with a face containing more than one boundary edge does not admit a dual dissection~$\dissection\dual$.
This prevents to use the definitions given in this section.
Although its accordion complex (resp.~zigzag complex) could still be defined as in~\cite{MannevillePilaud-accordion} (resp.~\cite{GarverMcConville}) for the disk, the resulting complexes would be join of smaller accordion complexes (resp.~zigzag complexes) defined in this paper.
See \cite[Prop.~2.4]{MannevillePilaud-accordion} for a detailed statement in the case of the disk.
\end{remark}

\section{All complexes coincide}

\vincent{This section is just sketched at the moment.}

\subsection{The bound quiver of a dissection}

\begin{definition}
\label{def:quiverDualDissections}
The bound quiver of a dissection~$\dissection$ is defined rotating around each face of~$\dissection$. Define also the blossoming quiver of~$\dissection$. Note that boundary edges of~$\dissection$ get two blossoms.
\end{definition}

\begin{proposition}
\label{prop:dualityKozul1}
For two dual dissections~$\dissection$ and~$\dissection\dual$ of an oriented surface, the quivers~$\bar Q(\dissection)$ and~$\bar Q(\dissection\dual)$ are Kozul duals.
\end{proposition}

\subsection{The surface of a quiver}

\begin{definition}
\label{def:surfaceQuiver}
The surface~$\surface(\bar Q)$ of a gentle bound quiver~$\bar Q = (Q,I)$ is obtained by glueing lozanges around arrows of~$Q$ following the rule given by the relations~$I$. The construction also automatically defines two dual dissections~$\dissection(\bar Q)$ and~$\dissection\dual(\bar Q)$ of the surface~$\surface(\bar Q)$.
\end{definition}

\begin{proposition}
\label{prop:dualityKozul2}
For any gentle bound quiver~$\bar Q$ with Kozul dual~$\bar Q\dual$, the surfaces~$\surface(\bar Q)$ and~$\surface(\bar Q\dual)$ coincide, but~$\dissection(\bar Q\dual) = \dissection\dual(\bar Q)$ and~$\dissection\dual(\bar Q\dual) = \dissection(\bar Q)$.
\end{proposition}

\subsection{Accordion, zigzag and non-kissing complexe coincide}

\begin{lemma}
\label{lem:walks=arcs}
Walks of $\bar Q$ are precisely arcs between blossom points.
\end{lemma}

\begin{lemma}
\label{lem:nonKissing=nonCrossing}
Non-kissing walks = non-crossing arcs.
\end{lemma}

\begin{theorem}
\label{thm:complexesCoincide}
\begin{itemize}
\item For any gentle bound quiver~$\bar Q$, the non-kissing complex~$\NKC$ is isomorphic to the accordion complex~$\AC[\dissection(\bar Q)]$ and to the zigzag complex~$\ZC[\dissection\dual(\bar Q)]$.
\item For any pair of dual dissections~$\dissection, \dissection\dual$ of an oriented surface, the accordion complex~$\AC$ and the zigzag complex~$\ZC$ are isomorphic to the non-kissing complex~$\NKC[\bar Q(\dissection)]$.
\end{itemize}
\end{theorem}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{alpha}
\bibliography{accordionComplexSurfaces}
\label{sec:biblio}
